---
title: "Final Project"
author: "Nuona Chen"
format: html
editor: visual
---

```{r}
library(jsonlite)
library(dplyr)
library(tidyr)
library(openintro)
library(nlme)
cms = read.csv("/Users/nuonachen/Downloads/Medicare_Physician_Other_Practitioners_by_Geography_and_Service_2020.csv")
spending = read.csv("/Users/nuonachen/Downloads/raw_data.csv")

```

```{r}
clean_data = cms %>% filter(Rndrng_Prvdr_Geo_Lvl != "National" & Rndrng_Prvdr_Geo_Cd != "") %>% left_join(select(spending, c("Total.Medicare.Part.A.and.or.Part.B.Program.Payments", "Location")), by = c("Rndrng_Prvdr_Geo_Desc" = "Location")) 

#names(clean_data)[names(clean_data) == 'Rndrng_Prvdr_Geo_Desc'] <- 'STATE'

#clean_data%>% left_join(select(tax, c("STATE", "A06500")), by = "STATE") 
clean_data["y"] = clean_data$Avg_Mdcr_Stdzd_Amt/clean_data$Avg_Sbmtd_Chrg

```

```{r}
write.csv(clean_data, "/Users/nuonachen/Downloads/clean_data.csv", row.names = FALSE)
```

```{r}
clean_data = read.csv("/Users/nuonachen/P3_files/clean_data_f.csv")
clean_data[clean_data$y > 1,]$y = 1
#clean_data = na.omit(clean_data)
```

![](data:image/png;base64,iVBORw0KGgoAAAANSUhEUgAAACgAAAAaCAYAAADFTB7LAAAAcElEQVR4Xu3OwQmAQAxE0bClWYCW5N06tM6V2YPg5CjoF/JhLoHAi6iqn9eOefUbqrYvHY0cQDLyAlKRNyARmYA0ZMLRkAlGQyaU72tkAtlim7r/vJqDUDjlKBROOQyFU2icQuMUGqfQuBEaV1XPOwEx96nYACK8+wAAAABJRU5ErkJggg== "Run Current Chunk")

```{r}
y= scale(clean_data$y, center = TRUE, scale = TRUE)
hist(y, main = "Distribution of Y")

qqnorm(y)
qqline(y)

y_ = scale(clean_data$y^(1/3), center = TRUE, scale = TRUE)
hist(y_, main = "Distribution of Cubic Root of Y", xlab = "Reimbursement Percentage")

qqnorm(y_)
qqline(y_)
#clean_data$y = scale(clean_data$y, center = T, scale = T)

#c = c("y", "Tot_Rndrng_Prvdrs", "Tot_Benes", "Tot_Srvcs", "Tot_Bene_Day_Srvcs", "Total.Medicare.Part.A.and.or.Part.B.Program.Payments","HCPCS_freq")
#clean_data[c] = clean_data %>% select(all_of(c)) %>% scale(center = TRUE, scale = TRUE)
```

```{r}
c = c( "y", "HCPCS_Drug_Ind", "Place_Of_Srvc", "Tot_Rndrng_Prvdrs", "Tot_Benes", "Tot_Srvcs", "Tot_Bene_Day_Srvcs", "Total.Medicare.Part.A.and.or.Part.B.Program.Payments","HCPCS_freq", "Rndrng_Prvdr_Geo_Desc")

clean_data = clean_data %>% select(all_of(c))%>% filter(Rndrng_Prvdr_Geo_Desc != "District of Columbia")
```

```{r}
library(vtable)
st(clean_data, group = "Rndrng_Prvdr_Geo_Desc",group.long = T, file = "/Users/nuonachen/Downloads/test") 

```

```{r}
library(ggplot2)
ggplot(aes(x = Rndrng_Prvdr_Geo_Desc, y= y), data = clean_data %>% filter(!is.na(Total.Medicare.Part.A.and.or.Part.B.Program.Payments))) + geom_boxplot() +  theme(axis.text.x = element_text(angle=90, vjust=1, hjust=1)) + ggtitle("Medicaid Reimbursement Percentage by State")+theme(plot.title = element_text(hjust = 0.5)) + xlab("States") + ylab("Medicaid Reimbursement Percentage")
```

```{r}
#ggplot(clean_data, aes(x = Tot_Rndrng_Prvdrs, y = y, color = Rndrng_Prvdr_Geo_Desc)) + geom_point(size = 2,show.legend = FALSE)

#ggplot(clean_data, aes(x = Tot_Rndrng_Prvdrs, y = y, color = Rndrng_Prvdr_Geo_Desc)) + geom_point(size = 2,show.legend = FALSE)

ggplot(aes(x = Tot_Rndrng_Prvdrs, y = y, color = Rndrng_Prvdr_Geo_Desc), data = clean_data) + geom_point(size= 2,show.legend = FALSE) + xlim(0, 1000)+facet_wrap(~ Rndrng_Prvdr_Geo_Desc) +  theme(
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +theme(
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())
```

```{r}
c = c( "y", "Tot_Rndrng_Prvdrs", "Tot_Benes", "Tot_Srvcs", "Tot_Bene_Day_Srvcs", "Total.Medicare.Part.A.and.or.Part.B.Program.Payments","HCPCS_freq")
clean_data[c] = clean_data %>% select(all_of(c)) %>% scale(center = T, scale = T)

```

#### 1. Hypothesis: The random effects associated with the State-specific intercepts is not significant.

```{r}
library(lme4)
m1= lme(y^(1/3)~ HCPCS_Drug_Ind + Place_Of_Srvc + Tot_Rndrng_Prvdrs +Tot_Benes+ Tot_Srvcs + Tot_Bene_Day_Srvcs + Total.Medicare.Part.A.and.or.Part.B.Program.Payments + HCPCS_freq, random = ~1 | Rndrng_Prvdr_Geo_Desc, clean_data, na.action=na.exclude, method = "REML")

#m1_= lmer(y^(1/3) ~ HCPCS_Drug_Ind + Place_Of_Srvc + Tot_Rndrng_Prvdrs +Tot_Benes+ Tot_Srvcs + Tot_Bene_Day_Srvcs + Total.Medicare.Part.A.and.or.Part.B.Program.Payments + HCPCS_freq + (1 | Rndrng_Prvdr_Geo_Desc), clean_data, na.action=na.exclude)

m2 = gls(y^(1/3) ~ HCPCS_Drug_Ind + Place_Of_Srvc + Tot_Rndrng_Prvdrs +Tot_Benes+ Tot_Srvcs + Tot_Bene_Day_Srvcs + Total.Medicare.Part.A.and.or.Part.B.Program.Payments + HCPCS_freq, clean_data, na.action = na.exclude, method = "REML")
```

```{r}
anova(m1, m2)
summary(m1)
```

p-value = 0.0001/2 \< 0.001. The test statistics L ratio is significant. Thus, we keep the random effects associated with STATE.

#### 2. Hypothesis: The variance of the residuals is constant for HCPCS_Drug_Ind and Place_Of_Srvc.

```{r}
m3 = lme(y^(1/3)~ HCPCS_Drug_Ind + Place_Of_Srvc + Tot_Rndrng_Prvdrs +Tot_Benes+ Tot_Srvcs + Tot_Bene_Day_Srvcs + Total.Medicare.Part.A.and.or.Part.B.Program.Payments + HCPCS_freq, random = ~1 | Rndrng_Prvdr_Geo_Desc, clean_data, na.action=na.exclude, method = "REML", weights = varIdent(form = ~1 | Place_Of_Srvc))

m4 = lme(y^(1/3)~ HCPCS_Drug_Ind + Place_Of_Srvc + Tot_Rndrng_Prvdrs +Tot_Benes+ Tot_Srvcs + Tot_Bene_Day_Srvcs + Total.Medicare.Part.A.and.or.Part.B.Program.Payments + HCPCS_freq, random = ~1| Rndrng_Prvdr_Geo_Desc, clean_data, na.action=na.exclude, method = "REML", weights = varIdent(form = ~1| Place_Of_Srvc*HCPCS_Drug_Ind))
anova(m3, m1)

anova(m1, m4)
```

```{r}
library(MuMIn)

r.squaredGLMM(m5)
plot(fitted(m4), resid(m4))
plot(m4)

mean((clean_data$y^(1/3) - fitted(m5))^2, na.rm = T)


summary(m5)

m6_full = lme(y^(1/3)~ HCPCS_Drug_Ind + Place_Of_Srvc + Tot_Rndrng_Prvdrs +Tot_Benes+ Tot_Srvcs + Tot_Bene_Day_Srvcs + Total.Medicare.Part.A.and.or.Part.B.Program.Payments + HCPCS_freq, random = ~1| Rndrng_Prvdr_Geo_Desc, clean_data, na.action=na.exclude, method = "ML", weights = varIdent(form = ~1| Place_Of_Srvc*HCPCS_Drug_Ind))

m6_reduced = lme(y^(1/3)~ HCPCS_Drug_Ind + Place_Of_Srvc + Tot_Rndrng_Prvdrs + Tot_Srvcs  + Total.Medicare.Part.A.and.or.Part.B.Program.Payments + HCPCS_freq, random = ~1| Rndrng_Prvdr_Geo_Desc, clean_data, na.action=na.exclude, method = "ML", weights = varIdent(form = ~1| Place_Of_Srvc*HCPCS_Drug_Ind))
anova(m6_full, m6_reduced)

m6_reduced = lme(y^(1/3)~ HCPCS_Drug_Ind + Place_Of_Srvc + Tot_Rndrng_Prvdrs + Tot_Srvcs  + Total.Medicare.Part.A.and.or.Part.B.Program.Payments + HCPCS_freq, random = ~1| Rndrng_Prvdr_Geo_Desc, clean_data, na.action=na.exclude, method = "REML", weights = varIdent(form = ~1| Place_Of_Srvc*HCPCS_Drug_Ind))

```

```{r}
plot(m6_reduced)
ggplot(data.frame(x=clean_data$HCPCS_freq,pearson=residuals(m6_reduced,type="pearson")),
      aes(x=x,y=pearson)) +
    geom_point(na.rm = T) + xlim(0, quantile(clean_data$Total.Medicare.Part.A.and.or.Part.B.Program.Payments)[4]) + 
    theme_bw() + xlab("HCPCS_freq") 
```

```{r}
means <- aggregate(clean_data[,c("Tot_Rndrng_Prvdrs","Tot_Srvcs", "Total.Medicare.Part.A.and.or.Part.B.Program.Payments", "HCPCS_freq")],by=list(clean_data$Rndrng_Prvdr_Geo_Desc),FUN=mean) %>% na.omit %>% filter(Group.1 != "District of Columbia")
lmcoefs <- summary(lm(y ~ Tot_Rndrng_Prvdrs + Tot_Srvcs + Total.Medicare.Part.A.and.or.Part.B.Program.Payments + HCPCS_freq+ Rndrng_Prvdr_Geo_Desc, data=clean_data, na.action = na.exclude))$coefficients[,"Estimate"]
means$effects <- c(0,lmcoefs[substr(names(lmcoefs),1,21) == "Rndrng_Prvdr_Geo_Desc"])
means$effects <- means$effects - mean(means$effects)
cor(means[,c("Tot_Rndrng_Prvdrs","Tot_Srvcs",'Total.Medicare.Part.A.and.or.Part.B.Program.Payments', "effects")])

```

```{r}
qqnorm(residuals(m6_reduced))
```

```{r}
library(reghelper)
library(lme4)
library(arsenal)
ICC(m6_reduced)


summary(m6_reduced)
random.effects(m6_reduced)
table_one <- tableby(Rndrng_Prvdr_Geo_Desc ~ ., data = clean_data %>% na.omit) 
summary_data = summary(table_one, title = "test")


```

```         
```
